Ten Simple Rules for Teaching Programming

### 2017-07-03 paper.tex
Moved the first few references across to BiBTeX

\documentclass{article}
\usepackage[a4paper]{geometry}
\begin{document}

@@

Guzdial refers to the belief that some people are born programmers and others aren't
as [computing's most enduring and damaging myth][guzdial-geek].
Our first and most important rule is that this is wrong:
competence at programming is not innate,
but is rather a learned skill that can be acquired and improved with practice.

The most powerful evidence for this comes from [Patitsas et al][patitsas].
They examined grade distributions in introductory computing courses at a large university,
and found that only 5.8% were actually multi-modal.
More damningly,
they found that computer science faculty were more likely to see distributions as bimodal
if they thought those grades came from a programming class
than if they believed the grades came from some other kind of class,
and that those faculty were even more likely to see the distributions as bimodal
if they believed some students are innately predisposed to do well in computer science.

@@

2.  Typing in boilerplate code that is needed by the lesson, but not
    directly relevant to it (such as library import statements), can
    distract learners from the intended thrust of a lesson.  As
    [Willingham][willingham] says, "Memory is the residue of thought";
    if the instructor spends their time typing boilerplate, that may
    be all that learners take away.

@@

[fixme-authentic-tasks]: cite-value-of-authentic-tasks
[fixme-cutts]: cutts-ref-for-peer-instruction
[fixme-live-coding]: cite-live-coding
[fixme-mazur]: cite-mazur-peer-instruction
[fixme-media-comp-replication]: cite-media-computing-replication
[fixme-outcomes]: cite-belief-in-innate-ability-shaping-outcomes
[fixme-parsons]: cite-parsons-problems
[fixme-transference]: cite-on-general-knowledge-transfer
[guzdial-geek]: https://cacm.acm.org/blogs/blog-cacm/189498-top-10-myths-about-teaching-computer-science/fulltext
[guzdial-media]: FIXME
[patitsas]: http://www.cs.toronto.edu/~sme/papers/2016/icer\_2016\_bimodal.pdf
[porter]: porter-et-al-peer-instruction
[sigcse]: FIXME
[willingham]: https://www.amazon.com/Why-Dont-Students-Like-School/dp/047059196X/

>>>>

\documentclass{article}
\usepackage[a4paper]{geometry}
\usepackage{natbib}
\usepackage{hyperref}
\begin{document}

@@

Guzdial refers to the belief that some people are born programmers and others aren't
as ``computing's most enduring and damaging myth'' \citep{guzdial-myths}.
Our first and most important rule is that this is wrong:
competence at programming is not innate,
but is rather a learned skill that can be acquired and improved with practice.

The most powerful evidence for this comes from \citet{patitsas-bimodal}.
They examined grade distributions in introductory computing courses at a large university,
and found that only 5.8\% were actually multi-modal.
More damningly,
they found that computer science faculty were more likely to see distributions as bimodal
if they thought those grades came from a programming class
than if they believed the grades came from some other kind of class,
and that those faculty were even more likely to see the distributions as bimodal
if they believed some students are innately predisposed to do well in computer science.

@@

2.  Typing in boilerplate code that is needed by the lesson, but not
    directly relevant to it (such as library import statements), can
    distract learners from the intended thrust of a lesson.  As
    \citet{willingham-book} says, "Memory is the residue of thought";
    if the instructor spends their time typing boilerplate, that may
    be all that learners take away.

@@

[fixme-authentic-tasks]: cite-value-of-authentic-tasks
[fixme-cutts]: cutts-ref-for-peer-instruction
[fixme-live-coding]: cite-live-coding
[fixme-mazur]: cite-mazur-peer-instruction
[fixme-media-comp-replication]: cite-media-computing-replication
[fixme-outcomes]: cite-belief-in-innate-ability-shaping-outcomes
[fixme-parsons]: cite-parsons-problems
[fixme-transference]: cite-on-general-knowledge-transfer
[guzdial-media]: FIXME
[porter]: porter-et-al-peer-instruction
[sigcse]: FIXME

\bibliographystyle{abbrvnat}
\bibliography{refs}
